Stat 400 Project

### 2021-11-23 Stat 400 proj.Rmd
created a function that gives new x,y coordinates of each individual after a given time period.

  #Assign starting positions randomly
  for(i in 1:num_subjects){
  start_x[i] <- runif(n=1, min=0, max=grid_x)
  start_y[i] <- runif(n=1, min=0, max=grid_y)
  }

@@

>>>>

  #Assign starting positions randomly
  for(i in 1:num_subjects){
  start_x[i] <- runif(n=1, min=0, max=x_dim)
  start_y[i] <- runif(n=1, min=0, max=y_dim)
  }

@@

#Function for getting updated coordinates
update_coords <- function(og_df, delta_df){
  new_mx <- matrix(data=NA, nrow=nrow(og_df), ncol=2)
  new_df <- data.frame(new_mx)
  new_df[,1] <- as.numeric(og_df[,'x']) + delta_df[,'delta_x']
  new_df[,2] <- as.numeric(og_df[,'y']) + delta_df[,'delta_y']
  colnames(new_df) <- c('x', 'y')
  return(new_df)
}
